%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.82, right=2.5cm]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.0cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
%\usepackage{hyperref}

\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt minus 0.1pt

\usepackage{float}
\usepackage{fontspec}
\newfontfamily\zhfont[BoldFont=Heiti SC Medium]{Heiti SC}
\newfontfamily\zhpunctfont{Heiti SC}
\usepackage{indentfirst}
\usepackage{zhspacing}
\zhspacing


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Panpan (盼盼)} % Your first name
\familyname{Xu (徐)} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{cv}
% \address{}{City, State 12345}
\mobile{+1 678 462 8619}
% \phone{}
% \fax{(000) 111 1113}
\email{pxu@cse.ust.hk}
\homepage{panpanxu.org}{panpanxu.org} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example

\extrainfo{\href{http://github.com/lliquid}{github}, \href{http://hk.linkedin.com/pub/panpan-xu}{linkedin}}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

\section{Summary}

\cvitem{}{I am a PhD candidate in Hong Kong University of Science and Technology. My research focus is in information visualization, esp. heterogeneous graph data visualization and visual analysis of social
media data. I am interested in combining analysis and interactive visualization techniques to gain insight into large and complex data. }

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2010--Now}{Ph.D Candidate, Computer Science}{Hong Kong University of Science and Technology}{}{}{}  % Arguments not required can be left empty
\cventry{2005--2009}{B.S., Computer Science}{Zhejiang University (Chu Kochen Honors College)}{}{}{}

\subsection{Ph.D Qualification Exam}

\cvitem{Title}{A Survey on Visual Analysis of Graphs}
\cvitem{Supervisor}{Prof. Huamin Qu}

\subsection{Bachelor's Thesis}
\cvitem{Title}{Physically Realistic Flow Simulation in Computer Animation}
\cvitem{Supervisor}{Prof. Xiaogang Jin}
\cvitem{}{\textit{Developed a prototype system for simulating and rendering visual effects of flows like smoke and fire, speeded by utilizing graphics hardwares.}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Internship and Visiting Experiences}
\cventry{Now}{Visiting Student}{Information Interface Lab (IILab) at Georgia Institute of Technology}{}{Mentor: Prof. John Stasko}{}
\cventry{2012-2013}{Research Intern}{Microsoft Research Asia}{}{Mentor: Dr. Yingcai Wu}{}


\section{Publications}

\cvitem{J-2013}{Visual Analysis of Topic Competition on Social Media. \textit{in IEEE Transactions on Visualization and Computer Graphics (accepted by IEEE Visual Analytics Science and Technology)}} 
\cvitem{} {\textbf{Panpan Xu}, Yingcai Wu, Enxun Wei, Tai-Quan Peng, Shixia Liu, Jonathan J.H. Zhu, Huamin Qu.}
\cvitem{} {\textit{Developed a framework combining text and time series analysis techniques with interactive visualization to gain insight into the dynamics of the users' influence and the competition among the topics for users' attention on social media.}}

\cvitem{J-2013}{Visual Analysis of Set Relations in a Graph. \textit{in Computer Graphics Forum (Proceedings of EuroVis)}}
\cvitem{} {\textbf{Panpan Xu}, Fan Du, Conglei Shi, Nan Cao, Hong Zhou, Huamin Qu.}
\cvitem{} {\textit{Developed visualization techniques to analyze the homophily effect in a social network, and proposed a set visualization method employing the metaphor of railway maps.}}

\cvitem{J-2013}{Edge Bundling in Information Visualization. in \textit{Tsinghua Science and Technology}}
\cvitem{}{Hong Zhou, \textbf{Panpan Xu}, Xiaoru Yuan, Huamin Qu}
\cvitem{}{Surveyed edge bundling techniques used to reduce edge cluttering and to facilitate connection pattern detection in graph drawing.}

\cvitem{J-2012}{RankExplorer: Visualization of Ranking Changes in Large Time Series Data.  \textit{in IEEE Transactions on Visualization and Computer Graphics (Proceedings of InfoVis)}}
\cvitem{}{Conglei Shi, Weiwei Cui, Shixia Liu, \textbf{Panpan Xu}, Wei Chen, Huamin Qu.}
\cvitem{}{Visualize the ranking change among a large number of items such as search phrases, which are ranked by their popularity and constantly changes overtime.}

\cvitem{C-2012}{Visualization of Taxi Drivers' Income and Mobility Intelligence. in \textit{International Symposium on Visual Computing}}
\cvitem{}{Yuan Gao, \textbf{Panpan Xu}, Lu Lu, He Liu, Siyuan Liu, Huamin Qu}

\cvitem{C-2011}{Visual analysis of people's mobility pattern from mobile phone data. in \textit{International Symposium on Visual Information Communication and Interaction}}
\cvitem{}{Jiansu Pu, \textbf{Panpan Xu}, Huamin Qu, Weiwei Cui, Siyuan Liu, Lionel M. Ni}


\section{Miscellaneous Projects}
\cvitem{2014} {Citation Visualization for VIS 25 Anniversary. Collaborated with IILab in Georgia Tech and developed visualizations for exploring and analyzing the publications in VIS conferences \href{http://www.cc.gatech.edu/gvu/ii/citevis/VIS25/}{\textbf{Demo}}}
\cvitem{2013} {Visual Analysis of Mobile Checkin Data. Collaborated with Huawei Noah's Ark Lab and developed an interactive visualization system for visualizing large scale spatial-temporal data}


\section{Technical Skills}

\cvitem{Languages} {Java, JavaScript, Python, C/C++, R}
\cvitem{Visualization Libs} {D3.js, Prefuse}
\cvitem{Graphics} {WebGL, OpenGL, Shader Language (GLSL)}
\cvitem{Others} {Version Control Systems (Git), Web Development (html, css, javascript), Databases (MySQL, SQLite), Graphic Design Softwares (Adobe Illustrator), etc.}


%----------------------------------------------------------------------------------------
%   TEACHING ASSISTANT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Teaching Assistant Experience}

\cvitem{2010-2013} {Design and Analysis of Algorithms}
\cvitem{2011, 2013} {Computer Graphics}
\cvitem{2010} {Object-Oriented Programming and Data Structures}


%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Scholarships}

\cvitem{2014}{HKUST Overseas Research Award}
\cvitem{2013}{VIS Doctoral Colloquim Student Travel Grant}
\cvitem{2010-2013}{HKUST Research/Teaching Assistant Studentship}
\cvitem{2006-2008}{Zhejiang University Academic Scholarships}
\cvitem{2007}{Mathematical Modeling Contest 1st Prize in Zhejiang Province}
\cvitem{2007}{The 5th Mathematical Modeling Contest of Zhejiang University, 2nd Prize}


\section{Professional Activities}

\cvitem{2013} {Doctoral Colloquium at VIS'13}
\cvitem{2013} {Student Volunteer at VIS'13}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitem{Chinese}{Mother tongue}
\cvitem{English}{Fluent (Toefl 104/120, taken in 2008)}


\clearpage

\end{document}