%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.86, right=1.8cm]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.0cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
%\usepackage{hyperref}

\usepackage{float}
\usepackage{indentfirst}



%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Panpan} % Your first name
\familyname{Xu} % Your last name

\mobile{+1(678)462-8619}
% \phone{}
% \fax{(000) 111 1113}
\email{panpan.xu@us.bosch.com}
% \homepage{panpanxu.org}{panpanxu.org} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example

% \extrainfo{\href{http://github.com/lliquid}{github: http://github.com/lliquid} \\\href{http://hk.linkedin.com/pub/panpan-xu}{linkedin: http://hk.linkedin.com/pub/panpan-xu}}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

\section{Summary}

\cvitem{}{I am now at Bosch Research North America as a Research Scientist in Visual Analytics. I finished my PhD thesis in Hong Kong University of Science and Technology. My research focus is in information visualization and visual analytics. Most of my research projects involve a combination of data mining and interactive visualization techniques.}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}
\cventry{2015.08-now} {Research Scientist} {Bosch Research and Technology Center North America}{Palo Alto, CA}{}{\begin{itemize}
\item Conduct research in visual analytics
\end{itemize}
}
\cventry{2015.01-08} {PostDoctoral Fellow} {Hong Kong University of Science and Technology}{Clear Water Bay, Hong Kong}{}{\begin{itemize}
\item Conduct research in visual analytics of graph structured data.
\item Mentor junior students on various visualization research projects.
\end{itemize}
}



\section{Education}

\cventry{2009-14}{Ph.D, Computer Science}{Hong Kong University of Science and Technology}{}{}{}  % Arguments not required can be left empty
\cvitem{}{Thesis: Visual Analysis of Heterogeneous and Dynamic Graphs}
\cvitem{}{Supervisor: Prof. Huamin Qu}
\cventry{2005-09}{B.S., Computer Science}{Zhejiang University (Chu Kochen Honors College)}{}{}{}


%\subsection{Ph.D Qualification Exam}
%\cvitem{Title}{A Survey on Visual Analysis of Graphs}
%\cvitem{Supervisor}{Prof. Huamin Qu}

%\subsection{Bachelor's Thesis}
%\cvitem{Title}{Physically Realistic Flow Simulation in Computer Animation}
%\cvitem{Supervisor}{Prof. Xiaogang Jin}
%\cvitem{}{\textit{Developed a prototype system for simulating and rendering visual effects of flows like smoke and fire, speeded by utilizing graphics hardwares.}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Scholarships}

\cvitem{2016}{Best Paper Honorable Mention Award, IEEE VisWeek (VAST, InfoVis, SciVis)}
\cvitem{2014}{Best Paper Award, International Symposium on Visual Information Communication and Interaction (VINCI)}
\cvitem{2014}{HKUST Overseas Research Award}
\cvitem{2013}{IEEE VisWeek (VAST, InfoVis, SciVis) Doctoral Colloquium Student Travel Grant}
\cvitem{2010-14}{HKUST Research/Teaching Assistant Studentship}
\cvitem{2006-08}{Zhejiang University Academic Scholarships (1st and 2nd Classes)}
\cvitem{2007}{Mathematical Modeling Contest 1st Prize in Zhejiang Province}
\cvitem{2007}{The 5th Mathematical Modeling Contest of Zhejiang University, 2nd Prize}


\section{Referred Journal Papers}

\cvitem{[J8]}{VisPubData.org: A Metadata Collection about IEEE Visualization (VIS) Publications. \textit{in IEEE Transactions on Visualization and Computer Graphics}, to appear}
\cvitem{}{Petra Isenberg, Florian Heimerl, Steffen Koch, Tobias Isenberg, \textbf{Panpan Xu}, Chad Stolper, Michael Sedlmair, Jian Chen, Torsten M\"{o}ller, John Stasko}

\cvitem{[J7, C8]}{ViDX: Visual Diagnostics of Assembly Line Performance in Smart Factories. \textit{in IEEE Transactions on Visualization and Computer Graphics (VAST 16)}, Best Paper Honorable Mention Award, to appear}
\cvitem{}{\textbf{Panpan Xu}, Honghui Mei, Liu Ren, and Wei Chen}

\cvitem{[C7]}{Interactive Visual Co-cluster Analysis of Bipartite Graphs. \textit{in IEEE Pacific Visualization Symposium (PacificVis)}, 2016}
\cvitem{}{\textbf{Panpan Xu}, Nan Cao, Huamin Qu, John Stasko}

\cvitem{[J6]}{Visualization of Bipartite Relations between Graphs and Sets. \textit{in Journal of Visualization}, 2014}
\cvitem{}{Hong Zhou, \textbf{Panpan Xu}, Huamin Qu}

\vspace{0.2cm}

\cvitem{[J5]}{MViewer: mobile phone spatiotemporal data viewer. \textit{in Frontiers of Computer Science}, 2014}
\cvitem{}{Jiansu Pu, Siyuan Liu, \textbf{Panpan Xu}, Huamin Qu, Lionel M. Ni}

\vspace{0.2cm}

\cvitem{[J4, C5]}{Visual Analysis of Topic Competition on Social Media. \textit{in IEEE Transactions on Visualization and Computer Graphics (VAST 13)}, 2013} 
\cvitem{} {\textbf{Panpan Xu}, Yingcai Wu, Enxun Wei, Tai-Quan Peng, Shixia Liu, Jonathan J.H. Zhu, Huamin Qu.}
\cvitem{} {Developed a framework combining \textit{text and time series analysis} techniques with \textit{interactive visualization} to gain insight into the dynamics of the competition among different topics for the public's attention \newline{} on \textit{social media}.\looseness=-1}

\vspace{0.2cm}

\cvitem{[J3, C4]}{Visual Analysis of Set Relations in a Graph. \textit{in Computer Graphics Forum (EuroVis 13)}, 2013}
\cvitem{} {\textbf{Panpan Xu}, Fan Du, Conglei Shi, Nan Cao, Hong Zhou, Huamin Qu.}
\cvitem{} {Developed visualization techniques to analyze the homophily effect in a \textit{social network}, and proposed a \textit{set visualization} method employing the metaphor of railway maps.}

\vspace{0.2cm}

\cvitem{[J2]}{Edge Bundling in Information Visualization. in \textit{Tsinghua Science and Technology}, 2013}
\cvitem{}{Hong Zhou, \textbf{Panpan Xu}, Xiaoru Yuan, Huamin Qu}
\cvitem{}{Surveyed edge bundling techniques used for edge clutter reduction and linkage pattern enhancement \newline{} in \textit{graph drawings} and \textit{parallel coordinate plots}.}

\vspace{0.2cm}

\cvitem{[J1, C3]}{RankExplorer: Visualization of Ranking Changes in Large Time Series Data.  \textit{in IEEE Transactions on Visualization and Computer Graphics (InfoVis 12)}, 2012}
\cvitem{}{Conglei Shi, Weiwei Cui, Shixia Liu, \textbf{Panpan Xu}, Wei Chen, Huamin Qu.}
\cvitem{}{Visualized the ranking change among a large number of items such as search phrases, which are ranked by their popularity and constantly change over time.}

\vspace{0.2cm}

\section{Referred Conference Papers}

\cvitem{[C6]}{Parallel Coordinates with Data Labels. \textit{in Proceedings of the 7th International Symposium on Visual Information Communication and Interaction (VINCI 14)}, \textbf{Best Paper Award}, 2014}
\cvitem{}{Hong Zhou, \textbf{Panpan Xu}, Zhong Ming, Huamin Qu}

\vspace{0.2cm}

\cvitem{[C2]}{Visualization of Taxi Drivers' Income and Mobility Intelligence. in \textit{International Symposium on Visual Computing}, 2012}
\cvitem{}{Yuan Gao, \textbf{Panpan Xu}, Lu Lu, He Liu, Siyuan Liu, Huamin Qu}

\vspace{0.2cm}

\cvitem{[C1]}{Visual analysis of people's mobility pattern from mobile phone data. in \textit{International Symposium on Visual Information Communication and Interaction}, 2011}
\cvitem{}{Jiansu Pu, \textbf{Panpan Xu}, Huamin Qu, Weiwei Cui, Siyuan Liu, Lionel M. Ni}

\vspace{0.2cm}

\section{Internship and Visiting Experiences}
\cvitem{2014}{Visiting Student, Information Interface Lab (IILab) at Georgia Institute of Technology \newline{} Mentor: Prof. John Stasko}
\vspace{0.2cm}
\cvitem{2012-13}{Research Intern, Microsoft Research Asia \newline{} Mentor: Dr. Yingcai Wu}

\section{Professional Activities}

\cvitem{} {Program Committee, IEEE Pacific Visualization Symposium (PacificVis) Papers 2017}
\cvitem{} {Program Committee, IEEE Pacific Visualization Symposium (PacificVis) Notes 2016}
\cvitem{} {Reviewer
\vspace{0.1cm}
\begin{itemize}
\item ACM SIGCHI
\item IEEE Transactions on Visualization and Computer Graphics
\item IEEE VIS (VAST and InfoVis)
\item The EG/VGTC Conference on Visualization (EuroVis)
\item IEEE Pacific Visualization Symposium (PacificVis)
\item IEEE Computer Graphics and Applications Magazine
\end{itemize}}
\cvitem{} {Doctoral Colloquium Presenter, IEEE VIS 2013}
\cvitem{} {Student Volunteer, IEEE VIS 2013}

\section{Misc Projects}
\cvitem{2014} {Citation Visualization VIS 25 Anniversary \newline{} (with Information Interface Lab in Georgia Tech, displayed at IEEE VIS conference)}
\cvitem{}{\begin{itemize}
\item Responsible for the visual design and the implementation of the demo
\item Visualization implemented with D3.js, underscore.js, and networkx graph library in Python
\item \href{http://www.cc.gatech.edu/gvu/ii/citevis/VIS25/}{Live at http://www.cc.gatech.edu/gvu/ii/citevis/VIS25/}
\end{itemize}}

\vspace{0.2cm}

\cvitem{2013} {Visual Analysis of Mobile Checkin Data (with Huawei Noah's Ark Lab).}
\cvitem{}{\begin{itemize}
\item Responsible for the overall design of the system
\item Large scale spatial-temporal data visualization
\item User behaviour analysis
\item Visualization implemented with Java, Prefuse visualization library and OpenStreetMap API
\end{itemize}}



\section{Technical Skills}

\cvitem{Languages} {Java, JavaScript, Python, C/C++, R, C\#}
\cvitem{Vis Toolkits} {D3.js, Prefuse}
\cvitem{Graphics} {WebGL, OpenGL, Shader Language (GLSL), CUDA (earlier versions)}
\cvitem{Others} {Version Control Systems (Git), Web Development (html, css, javascript), Front-end framework (React.js), Databases (MySQL, SQLite), Graphic Design Softwares (Adobe Illustrator), Visualization softwares (Tableau, Spotfire), etc.}


%----------------------------------------------------------------------------------------
%   TEACHING ASSISTANT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Teaching Experience}

\cvitem{2010-2013} {Design and Analysis of Algorithms, Teaching Assistant}
\cvitem{2011, 2013} {Computer Graphics, Teaching Assistant}
\cvitem{2010} {Object-Oriented Programming and Data Structures, Teaching Assistant}
\cvitem{}{The tasks of teaching assistant include leading tutorial and lab sessions of the course, designing exam questions, and grading homeworks.}


% \section{Course Taken in Graduate Study}

% \cvitem{} {Machine Learning}
% \cvitem{} {Advanced Algorithms}
% \cvitem{} {Advanced Computer Graphics}
% \cvitem{} {Computational Geometry}


%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------





%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

%\section{Languages}

%\cvitem{Chinese}{Mother tongue}
% \cvitem{English}{Fluent (Toefl 104/120, taken in 2008)}

% \section{References}

% \cvitem{Huamin Qu}{Associate Professor, Hong Kong University of Science and Technology}
% \cvitem{John Stasko}{Professor, Georgia Institute of Technology}
% \cvitem{Yingcai Wu}{Researcher, Microsoft Reseach Asia}
% \cvitem{Nan Cao}{Researcher, IBM T.J. Watson Research Center}

%\cvitem{}{Reference letters available upon request.}

\clearpage

\end{document}